A divergence between samples derived from the Kolmogorov-Smirnov statistic: specification, measures reference and example uses

### 2017-08-22 paper.tex
arrumadas tabelas de diferenca para apresentarem a estatistica de ks
termnado de incorporar a estatistica de KS nas medidas
initial files

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Distances between histograms]{A distance metric between histograms
derived from the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}

@@

\begin{abstract}
This document presents reference values for a distance metric
derived from the Kolmogorov-Smirnov test statistic $D_{F,F'}$.
Each measure of the $D_{F,F'}$ is a distance between two histograms.
This distance is normalized by the number of observations in each sample
to yield the $c=D_{F,F'}\sqrt{\frac{n n'}{n+n'}}$ statistic,
which can be mapped to p-values, i.e. values for which 
high enough levels of significance $\alpha$ implies the rejection of the null hypothesis.
Benchmarks for the implementation are delivered by comparing samples from known distributions.
Pattern examples in real data enables further
insight in the robustness and power of $c$.
\end{abstract}

@@

\FloatBarrier
\subsection{When the null hypothesis if false}
The null hypothesis is always false for a sufficiently small
significance level $\alpha$.
In this section,
each table holds a set comparisons between two samples:
one sample is generated through a
fixed distribution while the other
sample is modified in each comparison.
The comparison is repeated $N_c$ times.
The measures on $c$ chosen to report the results are:
the mean $\mu(c)$, the standard deviation $\sigma(c)$,
the median $m(c)$,
the  fraction
$\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
of rejection of the null hypothesis given the significance level $\alpha$.
The null hypothesis is true in the boldface lines.

\input{tables/tabNormDiff3_}
\input{tables/tabNormDiffMean_}
\input{tables/tabUniformDiffSpread_}
\input{tables/tabUniformDiffMean_}
\input{tables/tabWeibullDiffShape_}
\input{tables/tabPowerDiffShape_}
%\input{tables/tabNormDiff1}
%\input{tables/tabNormDiff2}

@@

\subsection{Changing the sample sizes}
Changing the number of elements in each sample
changes the value of the $c$ statistic.
This section is dedicated to tables in which
the $c$ statistic is given for two samples of varied sizes but
with fixed underlying distributions.
If a same value $\epsilon$ is changed of the mean $\mu$ or
the standard deviation, the first yields greater
values of the $c$ statistic.

>>>>

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Divergence between samples]{A divergence between samples
derived from the Kolmogorov-Smirnov statistic: specification, measures reference and example uses}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}

@@

\begin{abstract}
In this article, we describe reference values for a distance metric
derived from the Kolmogorov-Smirnov statistic $D_{F,F'}$.
Each measure of the $D_{F,F'}$ is a distance between two histograms.
This distance is normalized by the number of observations in each sample
to yield the $c=D_{F,F'}\sqrt{\frac{n n'}{n+n'}}$ statistic,
which can be mapped to p-values, i.e. values for which 
high enough levels of significance $\alpha$ implies the rejection of the null hypothesis.
Benchmarks for the implementation are delivered by comparing samples from known distributions.
Example application of the statistic for distinction of samples in real data enables further
insight in the robustness and power of $c$.
\end{abstract}

@@

\FloatBarrier
\subsection{When the null hypothesis if false}
The null hypothesis is always false for a sufficiently small
significance level $\alpha$.
In this section,
each table holds a set comparisons between two samples:
one sample is generated through a
fixed distribution while the other
sample is modified in each comparison.
The comparison is repeated $N_c$ times.
The measures on $c$ chosen to report the results are:
the mean $\mu(c)$, the standard deviation $\sigma(c)$,
the median $m(c)$,
the  fraction
$\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
of rejection of the null hypothesis given the significance level $\alpha$.
The null hypothesis is true in the boldface lines.
Let $D$ be the KS statistic when sample size goes to infinity.
Notably, high values of $c$ yield smaller $|D-D_{F,F'}|$,
i.e. more accurate estimates of $D$ through $D_{F,F'}$.

\input{tables/tabNormDiffDispersion_}
\input{tables/tabNormDiffMean_}
\input{tables/tabUniformDiffSpread_}
\input{tables/tabUniformDiffMean_}
\input{tables/tabWeibullDiffShape_}
\input{tables/tabPowerDiffShape_}
%\input{tables/tabNormDiff1}
%\input{tables/tabNormDiff2}

@@

\subsection{Changing the sample sizes}
Changing the number of elements in each sample
changes the value of the $c$ statistic.
This section is dedicated to tables in which
the $c$ statistic is given for two samples of varied sizes but
with fixed underlying distributions.
If a same value $\epsilon$ is changed of the mean $\mu$ or
the standard deviation, the first yields greater
values of the $c$ statistic.
In summary, raising the sample sizes raises $c$ and gives a value
of $D_{F,F'}$ closer to $D$ (the maximum difference between the theoretical cumulative distributions).
